Hydra Battles and Cie

### 2021-03-18 doc/chapter-primrec.tex
get around an issue with equations and modules

\begin{exercise}
The file \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack} presents two other definitions of the Ackermann functions based on the lexicographic ordering on $\mathbb{N}\times\mathbb{N}$.
Prove that all the four functions are extensionnally equal.
\end{exercise}

>>>>

\begin{exercise}
The file \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack} presents two other definitions\footnote{post on \href{https://stackoverflow.com/questions/10292421/error-in-defining-ackermann-in-coq} by Anton Trunov.} of the Ackermann functions based on the lexicographic ordering on $\mathbb{N}\times\mathbb{N}$.
Prove that all the four functions are extensionnally equal.
\end{exercise}
